On the validity of the Born approximation for beyond-Gaussian weak lensing observables

### 2016-11-23 Paper/paper.tex
incorporated suggestions

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{Figures/bias_ngal_convergence_momentsSN_s50_nb9.eps}
\end{center}
\caption{Parameter bias dependence on the galaxy density angular $n_g$ used to compute the shape noise rms in eq. (\ref{par:shaperms}). The plotted quantity is the difference between the mean of 1000 parameter fits using the estimator (\ref{par:fisherest}) with $\bb{M}$ measured with and without the Born approximation. The difference is shown in units of the estimator standard deviation. We show the trend for $\Omega_m$ (blue), $w_0$ (red) and $\sigma_8$ (green).}
\label{fig:parbiasSN}
\end{figure}

@@

\section{Discussion}
\label{sec:discuss}
% 
In this section, we discuss our main findings. Figure \ref{fig:csample} shows that the dominant post--Born correction to the $\kappa$ reconstruction comes from the geodesic term (eq.~\ref{sim:gp}). This can be seen by looking at the lens-lens term, which is aver an order of magnitude smaller than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map. 
%ZH: I changed above to ``over an order of magnitude''

@@

\begin{itemize}
\item The lowest--order post--Born corrections to the convergence power spectrum, skewness and kurtosis are sufficient to fully account for the discrepancies between ray--tracing and the Born approximation.
\item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
%ZH: Added memory above. OK?
\item The $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case.
\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet in the noiseless case. However, this bias becomes negligible when galaxy shape noise is added, due to an increased scatter in parameter estimates.   
\end{itemize}
%
Future prospects involve study the Born approximation validity for CMB lensing observations. 
%ZH(***): we should add 2-3 sentences here, saying that we expect Born approximation to fail more badly in CMB lensing, and cite papers that recently showed this already (e.g. by Anthony Lewis).   You could steal this from the discussion section of our recent CMB lensing paper (with Jia, Colin, etc).

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{Figures/bias_ngal_convergence_momentsSN_s50_nb9.eps}
\end{center}
\caption{Parameter bias dependence on the galaxy density angular $n_g$ used to compute the shape noise rms in eq. (\ref{par:shaperms}). The plotted quantity is the difference between the mean of 1000 parameter fits using the estimator (\ref{par:fisherest}) with $\bb{M}$ measured with and without the Born approximation. The difference is shown in units of the estimator standard deviation. We show the trend for $\Omega_m$ (blue), $w_0$ (red) and $\sigma_8$ (green).}
\label{fig:parbiasSN}
\end{figure}

@@

\section{Discussion}
\label{sec:discuss}
% 
In this section, we discuss our main findings. Figure \ref{fig:csample} shows that the dominant post--Born correction to the $\kappa$ reconstruction comes from the geodesic term (eq.~\ref{sim:gp}). This can be seen by looking at the lens-lens term, which is aver an order of magnitude smaller than the geodesic term, and by looking at the full $\kappa-\kappa_{\rm born}$ residuals, which show a very similar overall level, as well as structural detail, to the ones found in the $\kappa_{\rm geo}$ map. The reader might have noticed the curious alignment feature in Figure \ref{fig:csample}, in which all the dipolar structures in $\kappa_{\rm geo}$ appear to be horizontally aligned throughout the field of view. We believe that this alignment is not a numerical effect, but is originated physically by the $\nabla\delta$ terms in eq.~(\ref{sim:gp}). Early in the line--of--sight integration, the field of view covers a very small section of the simulation box ($\sim7\,{\rm Mpc}$ for the first lens), within which dipolar structures are aligned. These alignments survive after the full integration is completed due to the $\nabla\delta\cdot\nabla\Phi$ term, which couples lenses at different redshifts. To provide evidence that the closest lenses to the observer are responsible for the alignment features, we performed the line--of--sight integration for $\kappa_{\rm geo}$ by rotating the first 5 lenses by 90 degrees. This is sufficient to coherently flip the dipolar structures from horizontal to vertical throughout the field of view.
%ZH: I changed above to ``over an order of magnitude''

@@

\begin{itemize}
\item The lowest--order post--Born corrections to the convergence power spectrum, skewness and kurtosis are sufficient to fully account for the discrepancies between ray--tracing and the Born approximation.
\item Using the \ttt{LensTools} software package, Born integration costs 4 times less than ray--tracing, and consumes about half as much memory.
%ZH: Added memory above. OK?
\item The $\kappa$ power spectrum leads to negligible parameter bias for an LSST--like survey, even in the noiseless case.
\item Fitting an observation with Born--approximated higher $\kappa$ moments leads to significant bias in the $(\Omega_m,w_0,\sigma_8)$ triplet in the noiseless case. However, this bias becomes negligible when galaxy shape noise is added, due to an increased scatter in parameter estimates. This conclusion holds even for future space--based surveys that can probe galaxy angular densities as high as $60\,{\rm arcmin}^{-2}$.    
\end{itemize}
%
In this work we examined the validity of the Born approximation for WL galaxy surveys, but a similar study could in principle be carried for the lensing potential reconstruction from CMB temperature and polarization data. Lensing of the CMB probes structures over a wider range of redshifts and hence CMB lensing observables can be expected to be more Gaussian distributed than their galaxy lensing counterparts. This suggests the possibility that non--Gaussian features in CMB lensing data could come from post--Born corrections of $O(\Phi^2)$ rather than inherent non--Gaussianity in the Born $O(\Phi)$ terms. This possibility has been suggested by \citep{CMBPrattenLewis}, who looked at the CMB lensing $\kappa$ bi--spectrum. Because of the high significance with which non--Gaussianities in the CMB lensing potential can be detected with future Stage IV experiments \citep{CMBLNG}, we propose to investigate post--Born corrections to CMB lensing observables in future work.

%ZH(***): we should add 2-3 sentences here, saying that we expect Born approximation to fail more badly in CMB lensing, and cite papers that recently showed this already (e.g. by Anthony Lewis).   You could steal this from the discussion section of our recent CMB lensing paper (with Jia, Colin, etc).
%AP: does this work?
